Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning

### 2021-03-07 paper/main.tex

\subsection{False discovery and power for dimension reduction}
\citep{taeb_false_2020}

\subsection{Random-projection ensemble classification}
We now describe random-projection ensemble classification as proposed by \citet{cannings_random-projection_2017}, a flexible tool which allows the use of a practitioner's favourite low-dimensional classifier. Random-projection ensemble classification will form the basis of our Let $X$ be a random vector taking values in $\mathcal{X} \subset \mathbb{R}^p$ from which we are attempting to predict a response $Y$ taking values in $\{0,1\}$. Furthermore suppose we are given $n$ observations of the pair, and denote our data $\mathcal{T}_n = \{(x_1, y_1), (x_2, y_2), \dots, (x_n, y_n)\}$. We choose a $d$-dimensional base classifier $C$, and for any projection $A:\mathbb{R}^p \rightarrow \mathbb{R}^d$ denote by $C^A$ that classifier applied to the projected observations $AX$ (so the prediction $C^A(x) = C(Ax)$). We write $\mathcal{T}_n^A$ for the projected dataset $\{(Ax_1, y_1), (Ax_2, y_2), \dots, (Ax_n, y_n)\}$. Then we may let $C^A_{\mathcal{T}_n^A}$ denote the classifier trained on the projected dataset and acting as a classifier on $\mathbb{R}^p$.

@@

\section{Simulations}

\subsection{Sparse class boundaries}
Here we let 
\[X \ | \ \{Y = 0\} \sim \frac{1}{2}N_p(\mu_0, \Sigma) + \frac{1}{2}N_p(-\mu_0, \Sigma) \]
\[X \ | \ \{ Y = 1\} \sim \frac{1}{2}N_p(\mu_1, \Sigma) + \frac{1}{2}N_p(-\mu_1, \Sigma) \]

@@

\[X \ | \ \{Y=0\} \sim N_p(\Omega_p\mu_0, \Omega_p \Sigma_0 \Omega_p^T)  \] 
\[X \ | \ \{Y = 1\} \sim N_p(\Omega_p\mu_1, \Omega_p\Sigma_1\Omega_p^T)  \]

\begin{figure}
    \centering
    \includegraphics[width=6in]{../results/figures/sim_evs.png}
    \caption{Caption}
    \label{fig:sim1_ev}
\end{figure}

>>>>

\subsection{False discovery and power for dimension reduction}
We use the definitions from \citet{taeb_false_2020} of false discovery and power for subspace discovery. In particular, given a target subspace $S^* \subset \mathbb{R}^p$, and an estimate subspace $\hat{S}$, we let the false discovery $FD$ be given by 
\[FD = \mathrm{Trace} \big( (I_p - \Pi_{S^*})\Pi_{\hat{S}} \big) \]
and power
\[PW = \mathrm{Trace} \big( \Pi_{S^*} \Pi_{\hat{S}} \big). \]
Here, $\Pi_{S^*}, \Pi_{\hat{S}}$ refer to projections onto $S^*$ and $\hat{S}$ respectively. 
\subsection{Random-projection ensemble classification}
We now describe random-projection ensemble classification as proposed by \citet{cannings_random-projection_2017}, a flexible tool which allows the use of a practitioner's favourite low-dimensional classifier. Random-projection ensemble classification will form the basis of our Let $X$ be a random vector taking values in $\mathcal{X} \subset \mathbb{R}^p$ from which we are attempting to predict a response $Y$ taking values in $\{0,1\}$. Furthermore suppose we are given $n$ observations of the pair, and denote our data $\mathcal{T}_n = \{(x_1, y_1), (x_2, y_2), \dots, (x_n, y_n)\}$. We choose a $d$-dimensional base classifier $C$, and for any projection $A:\mathbb{R}^p \rightarrow \mathbb{R}^d$ denote by $C^A$ that classifier applied to the projected observations $AX$ (so the prediction $C^A(x) = C(Ax)$). We write $\mathcal{T}_n^A$ for the projected dataset $\{(Ax_1, y_1), (Ax_2, y_2), \dots, (Ax_n, y_n)\}$. Then we may let $C^A_{\mathcal{T}_n^A}$ denote the classifier trained on the projected dataset and acting as a classifier on $\mathbb{R}^p$.

@@

\section{Simulations}
We present two simulation studies, of distributions with known central subspaces, and compare our method with other techniques for supervised dimension reduction. 
\subsection{Sparse class boundaries}
Here we let 
\[X \ | \ \{Y = 0\} \sim \frac{1}{2}N_p(\mu_0, \Sigma) + \frac{1}{2}N_p(-\mu_0, \Sigma) \]
\[X \ | \ \{ Y = 1\} \sim \frac{1}{2}N_p(\mu_1, \Sigma) + \frac{1}{2}N_p(-\mu_1, \Sigma) \]

@@

\[X \ | \ \{Y = 0\} \sim N_p(\Omega_p\mu_0, \Omega_p \Sigma_0 \Omega_p^T)  \] 
\[X \ | \ \{Y = 1\} \sim N_p(\Omega_p\mu_1, \Omega_p\Sigma_1\Omega_p^T)  \]

\begin{figure}
    \centering
    \includegraphics[width=6in]{../results/figures/sim_evs.png}
    \caption{Caption}
    \label{fig:sim_evs}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=6in]{../results/figures/sim_rvs.png}
    \caption{Caption}
    \label{fig:sim_rvs}
\end{figure}
